Democracy, Public Support, and Measurement Uncertainty

### 2021-05-04 paper/dcpo_demsupport.Rmd
writing a customized version of glance for plm

# load all the packages you will use below 
p_load(
  dataverse, # data scraping
  DCPOtools,
  boot, plm, # analysis
  flextable, 
  kableExtra, modelsummary, # tabulation
  gridExtra,
  latex2exp, # visualization
  rstan, # Bayesian estimation
  broomExtra, tidyverse, janitor, glue, # data wrangling
  drhutools,
  dotwhisker # visualization
)

@@

glance_result_cls <- map(df_result_cls, glance)

@@

#save(df_result_cls, file = here::here("output", "estimates_clsMeanAJPS.RDS"))
```

@@

# estimate_dcpo <- function(aModel, aType = "pooling") {
#   if (aType == "gmm") {
#     result_dcpo_1k <- map(df_dcpo, function(aDataset) {
#       pgmm(
#         as.formula(aModel),
#         effect = "individual",
#         model = "onestep",
#         transformation = "ld",
#         indexes = c("Country", "Year"),
#         data = aDataset
#       )
#     })
#     
#     result_vars_dcpo_1k <-
#       mitools::MIextract(result_dcpo_1k, fun = vcovHC_se)
#     
#   } else {
#     result_dcpo_1k <- map(df_dcpo, function(aDataset) {
#       plm::plm(aModel,
#                model = "pooling",
#                data = aDataset)
#     })
#     
#     result_vars_dcpo_1k <-
#       mitools::MIextract(result_dcpo_1k, fun = vcovBK_se)
#   }
#   
#   result_betas_dcpo_1k <-
#     mitools::MIextract(result_dcpo_1k, fun = coef)
#   
#   df_result_dcpo <-
#     summary(
#       mitools::MIcombine(results = result_betas_dcpo_1k, variance = result_vars_dcpo_1k)
#     ) %>% rownames_to_column(var = "term") %>%
#     rename(conf.low = `(lower`,
#            conf.high = `upper)`,
#            estimate = results) %>%
#     filter(!str_detect(term, "(Intercept)"))
# }
# 
# mod_ls <- paste0(
#   "Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + ", 
#   c("plm::lag(theta, 1)", 
#     "plm::lag(theta_dem, 1) + plm::lag(theta_aut, 1) "), 
#   " + plm::lag(lg_imp_mdpgdp, 1) +
#              plm::lag(mdprgdp_grwth, 1) + plm::lag(Region_libdem, 1) +
#              plm::lag(muslism_prop_2010, 1) + plm::lag(dependence_pc_di, 1)"
# )
# 
# df_result_dcpoAJPS <- map(mod_ls, estimate_dcpo)

@@

load(here::here("output", "estimates_clsMeanAJPS.RDS"))
load(here::here("output", "estimates_clsAJPS.RDS"))
load(here::here("output", "estimates_dcpoAJPS.RDS"))

>>>>

# load all the packages you will use below 
p_load(
  dataverse, # data scraping
  DCPOtools, mitools,
  boot, plm, # analysis
  flextable, 
  broomExtra, kableExtra, modelsummary, # tabulation
  gridExtra,
  latex2exp, # visualization
  rstan, # Bayesian estimation
  tidyverse, janitor, glue, # data wrangling
  drhutools,
  dotwhisker # visualization
)

@@

glance_result_cls <- map(df_result_cls, function(aResult){
  if(class(aResult) == "plm"){ 
    glance.plm(aResult) # using the customized glance function
  }else{
      glance(aResult)
    }
})

@@

save(tidy_result_cls, glance_result_cls, file = here::here("output", "estimates_clsMeanAJPS.RDA"))
```

@@

@@

load(here::here("output", "estimates_clsMeanAJPS.RDA"))
load(here::here("output", "estimates_clsAJPS.RDS"))
load(here::here("output", "estimates_dcpoAJPS.RDS"))
